On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-03-03 engineering.tex
complete def infosec-confidentiality and example

\subsection{Elicitation of Security Requirements}\label{sec:properties}
In \autocite{Anderson1972report,Samonas2014cia}, CIA are defined as follows.
\begin{itemize}
	\item Unauthorized information release: an unauthorized person is able
		to read and take  advantage  of  information  stored  in  the
		computer.  This  category of concern  sometimes  extends  to
		``traffic  analysis,''  in  which  the intruder  only observes
		the  patterns  of  information  use.  From  those patterns,
		the  intruder can   infer   some   information   content.
		This category   also   includes   the unauthorized use of a
		proprietary program.  (Confidentiality or Secrecy) 
	\item Unauthorized  information  modification:  an  unauthorized person
		is  able  to make changes in stored information –a form  of
		sabotage.  It should be noted that in the case of this kind of
		violation, the intruder does not necessarily see the
		information he has changed.  (Integrity)
	\item Unauthorized  denial  of  use:  an  intruder  can  prevent  an
		authorized  user  from referring to, or from modifying
		information, even though the intruder may not be able to refer
		to, neither modify the information themselves. (Availability)
\end{itemize}

We now want to generalize the CIA triad to agents and not just 
information and map it to the $\abftheory$ theory.
\begin{definition}{\bf Infosec-Confidentiality --}\label{def:infosec-c}
	An Information $\varphi$ is considered to be confidential over a set of
	agents $Ag_c$ if, per each agent $a\in Ag_c$, the content of the
	information (i.e. the data it carries) can only be understood (i.e. the relation
	between the information and its data can be known) by the
	agents in $Ag_c$.

	\begin{itemize}
		\item[$(\interpretation21)$]
			for all agents $a\in Ag$, $\world\models\information{a}{\varphi}$ and
			$\world\models\rcc(\varphi,Conf) \wedge \neg\dr{Conf}{\varphi}$ iff
			$\world\models\knows{x}{[\information{a'}{\varphi}\rightarrow\varphi]}$
			for any agent $a'$ such that $a'\not\in Ag_c$
	\end{itemize}
\end{definition}

>>>>

\subsection{Elicitation of Security Requirements}\label{sec:properties}
In \autocite{Anderson1972report,Samonas2014cia}, CIA are defined as follows.
\begin{itemize}
	\item Unauthorized information release: an unauthorized person is able
		to read and take  advantage  of  information  stored  in  the
		computer.  This  category of concern  sometimes  extends  to
		``traffic  analysis,''  in  which  the intruder  only observes
		the  patterns  of  information  use.  From  those patterns,
		the  intruder can   infer   some   information   content.
		This category   also   includes   the unauthorized use of a
		proprietary program.  (Confidentiality or Secrecy) 
	\item Unauthorized  information  modification:  an  unauthorized person
		is  able  to make changes in stored information -- a form  of
		sabotage.  It should be noted that in the case of this kind of
		violation, the intruder does not necessarily see the
		information he has changed.  (Integrity)
	\item Unauthorized  denial  of  use:  an  intruder  can  prevent  an
		authorized  user  from referring to, or from modifying
		information, even though the intruder may not be able to refer
		to, neither modify the information themselves. (Availability)
\end{itemize}

We now want to generalize the CIA triad to agents and not just 
information and map it to the $\abftheory$ theory.
\begin{definition}{\bf Infosec-Confidentiality --}\label{def:infosec-c}
	An Information $\varphi$ is considered to be confidential to a set of 
	agents $Ag_c$ if, per each agent $a\in Ag_c$, the content of the
	information (i.e. the data it carries) can only be understood (i.e. the relation
	between the information and its data can be known) by the
	agents in $Ag_c$.

	\begin{itemize}
		\item[$(\interpretation21)$] for all agents $a\in Ag$,
			$\world\models\information{a}{\varphi}$ and
			$\world\models\rcc(\varphi,Conf) \wedge
			\neg\dr{Conf}{\varphi}$ iff for any world $\world'$
			such that $\world \modalrelation\world'$,
			$\world'\models\believe{a}{\varphi}$, and
			$\world'\models\knows{a}{\exists f.~
			f(\information{a}{\varphi})=\varphi}$, where 
			$Conf$ is a Region and $f$ is an uninterpreted function.
	\end{itemize}
\end{definition}

\begin{example}{Dummy security protocol --}
	The last part (part III) of the protocol in our first example
	(Figure~\ref{fig:protocol-example}) represents the actual key exchange
	which, in general, needs to be confidential; otherwise the key would be
	known by any other agent who can, e.g., read on the communication
	channel.  Therefore, the last message, in Alice-and-Bob notation can be
	rephrased as: \begin{displaymath} Alice\Rightarrow Bob: enc(pk(Bob),
	symmetricKey) \end{displaymath} where $enc$ is the standard asymmetric
	encryption operator that encrypts the message $symmetricKey$ with the
	public key of Bob $pk(Bob)$ (see, e.g.,
	\autocite{Rocchetto2017interpolation} for a detailed formalization).
	The function $f$ in Definition~\ref{def:infosec-c}, represents any
	function used to enforce confidentiality on information.  In this
	example, $f$ is identified with $enc$ (i.e.
	$enc(pvt(Bob),symmetricKey)=symmetricKey$), the information is
	$\information{Alice}{[enc(pk(Bob),symmetricKey)]}$ and the data, i.e.
	$\varphi$ in Definition~\ref{def:infosec-c}, is $\varphi=symmetricKey$.
	In the perfect cryptography assumption, and assuming for simplicity
	that the logic of the whole protocol preserves confidentiality, the
	message is confidential. In fact, if $Ag={Alice, Bob}$ and $\eq{symmetricKey}{Conf}$:
	\begin{align*}
		\world^0\models\belief{Alice}{symmetricKey},\\
		\world^1\models\information{Alice}{symmetricKey}, \text{and}\\
		\world^2\models\belief{Bob}{symmetricKey} ~\text{if} \\
		enc(pvt(Bob), \information{Alice}{symmetricKey}=symmetricKey)=symmetricKey\\
		(i.e. f=enc ~\text{and}~ \information{Alice}{symmetricKey}=enc(pub(Bob),symmetricKey))\\
	\end{align*}
\end{example}
